Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-02-15 scagnostics.Rmd
updates to intro

Scagnostics are scatterplot diagnostics. They were primarily developed to extract pairs of interesting variables from a large collection. XXX (Ursula to fill in based loosely on material at the German language wikipedia page - it would be good to translate this page and provide an English version on wikipedia)

*** Explanation of tour algorithm and projection pursuit and software

@@

>>>>

Scagnostics are scatterplot diagnostics. They were primarily developed to extract pairs of interesting variables from a large collection. XXX (Ursula to fill in based loosely on material at the German language wikipedia page - it would be good to translate this page and provide an English version on wikipedia). Scagnostics are available in two R packages [@LWscagR] and [@HWscagR]. This work is built upon the scagnostics package by @HWscagR because the underlying base is built using C, works across platforms.

Projection pursuit is typically 
*** Explanation of tour algorithm and projection pursuit and software

@@

The projectionpursuitindex, a function of all possible projections
of the data, invariablyhas many "hills and valleys" and "knife-edgeridges"because of
the varying shape of underlyingdensity estimates from one projectionto the next.

The paper is accompanied by the R package "binostics" available on CRAN, and new indices have been implemented in the "tourr" package.
